---
title: "Stock Back Test 5.0"
author: "Ethan"
output:
  html_document:
    df_print: paged
    toc: yes
    theme: yeti
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.pos = 'H', echo = FALSE, message = FALSE, warning = FALSE)
```

```{r}
library(knitr)
library(ggplot2)
library(quantmod)
library(tidyverse)
library(DT)
library(tidyquant)
```

# Rules

If the open price higher than the lowest price of the last trade date, then buy it and sell at the close price unless the price hits the stop loss price, which is the same as the lowest price of the last trade date.

```{r}
BackTest = function(stock_code, stock_start, stock_end, stock_interval = 'daily', 
                    adj = TRUE, fix = TRUE, method = "beginning", fix_loss = 0.03, loss_margin = 0)
{
  # Import data
  dat <- getSymbols(stock_code, from = stock_start, to = stock_end, 
                    auto.assign=FALSE, periodicity = stock_interval)
  cat(stock_code, stock_interval, "from", stock_start, "to", stock_end)
  
  # Format Changing
  dat = data.frame(date=index(dat), coredata(dat))
  dat = dat[, 1:6]
  names(dat) = c("trade_date", "open", "high", "low", "close", "volume")
  
  # Data Cleaning
  dat = filter(dat, open != high | high != low | low != close)
  dat = dat[complete.cases(dat), ]
  
  # Change date format
  dat$trade_date = as.Date(dat$trade_date, "%Y-%m-%d")
  
  # Tactic: bought or not and cost if bought
  bought = c(FALSE)
  cost = c(NA)
  if(method == "beginning")
  {
    for(i in 2:nrow(dat))
    {
      if(dat$open[i] > dat$low[i-1])
      {
        bought = c(bought, TRUE)
        cost = c(cost, dat$open[i])
      }
      else
      {
        bought = c(bought, FALSE)
        cost = c(cost, NA)
      }
    }
  }
  if(method == "end")
  {
    for(i in 2:nrow(dat))
    {
      bought = c(bought, TRUE)
      cost = c(cost, dat$close[i-1])
    }
  }
  dat = cbind(dat, bought, cost)
  
  # Tactic: sell price
  sell = c(NA)
  for(i in 2:nrow(dat))
  {
    if(dat$bought[i] == TRUE)
    {
      sell = c(sell, dat$close[i])
    }
    else
    {
      sell = c(sell, NA)
    }
  }
  dat = cbind(dat, sell)
  
  # Tactic: trigger
  trigger = c("none")
  if(fix == FALSE)
  {
    for(i in 2:nrow(dat))
    {
      if(dat$bought[i] == TRUE & dat$cost[i] <= dat$low[i-1] + (dat$high[i-1] - dat$low[i-1]) * 0.5 & dat$low[i] < dat$low[i-1] * (1 - loss_margin))
      {
        trigger = c(trigger, "stop_loss_low_point")
        dat$sell[i] = min(dat$low[i-1] * (1 - loss_margin), dat$open[i])
      }
      else if(dat$bought[i] == TRUE & dat$cost[i] > dat$low[i-1] + (dat$high[i-1] - dat$low[i-1]) * 0.5 & dat$low[i] < (dat$low[i-1] + (dat$high[i-1] - dat$low[i-1]) * 0.5) * (1 - loss_margin))
      {
        trigger = c(trigger, "stop_loss_middle_point")
        dat$sell[i] = min((dat$low[i-1] + (dat$high[i-1] - dat$low[i-1]) * 0.5) * (1 - loss_margin), dat$open[i])
      }      
      else if(dat$bought[i] == TRUE)
      {
        trigger = c(trigger, "within")
      }
      else
      {
        trigger = c(trigger, "none")
      }
    }
  }
  if(fix == TRUE)
  {
    for(i in 2:nrow(dat))
    {
      if(dat$bought[i] == TRUE & dat$open[i] < dat$cost[i] * (1 - fix_loss))
      {
        trigger = c(trigger, "stop_loss_fix_open")
        dat$sell[i] = dat$open[i]       
      }
      else if(dat$bought[i] == TRUE & dat$low[i] < dat$cost[i] * (1 - fix_loss))
      {
        trigger = c(trigger, "stop_loss_fix")
        dat$sell[i] = dat$cost[i] * (1 - fix_loss)    
      }
      else if(dat$bought[i] == TRUE)
      {
        trigger = c(trigger, "within")
      }
      else
      {
        trigger = c(trigger, "none")
      }
    }
  }
  trigger = as.factor(trigger)
  dat = cbind(dat, trigger)
  
  # Margin and Margin rate
  margin = NA
  dat = cbind(dat, margin)
  for(i in 1:nrow(dat))
  {
    if(dat$bought[i] == TRUE)
    {
      dat$margin[i] = dat$sell[i] - dat$cost[i]
    }
  }
  margin_rate = NA
  dat = cbind(dat, margin_rate)
  for(i in 1:nrow(dat))
  {
    if(dat$bought[i] == TRUE)
    {
      dat$margin_rate[i] = (dat$sell[i] - dat$cost[i]) / dat$cost[i]
    }
  }
  
  # Plot: Margin
  dat_margin = dat %>% 
    filter(bought == TRUE)
  p_margin = ggplot(dat_margin) +
    geom_point(mapping = aes(x = trade_date, y = margin_rate)) +
    geom_abline(slope = 0, intercept = 0, color = "red")
  
  # Plot: buy and sell points
  p_points = dat %>% 
    ggplot(aes(x = 1:nrow(dat), y = close)) +
    geom_candlestick(aes(open = open, high = high, low = low, close = close), 
                     colour_up = "tomato", colour_down = "green",
                     fill_up = "tomato", fill_down = "green") +
    geom_point(aes(y = cost), shape = 3) +
    geom_point(aes(y = sell), shape = 4) +
    theme_tq()

  # Summary
  sum_trigger = summary(trigger)
  margin = sum(dat$margin, na.rm = TRUE)
  market = dat$close[nrow(dat)] - dat$close[1]
  sum_margin = data.frame(margin = round(margin, 3),
                          margin_rate = round(margin / mean(dat$close), 3),
                          market = market,
                          market_rate = round(market / mean(dat$close), 3))
  
  # Digits
  dat$margin = dat$margin %>% 
    round(3)
  dat$margin_rate = dat$margin_rate %>% 
    round(3)
  
  # Return
  outcome = list("data" = dat, "sum_trigger" = sum_trigger, "sum_margin" = sum_margin, 
                 "p_margin" = p_margin, "p_points" = p_points)
  return(outcome)
}
```

# 报告

## 各种股票周K表现

```{r}
stock_start = "2010-01-01"
stock_end = "2019-11-07"
stock_code = c("^IXIC", "^GSPC", "^DJI", "^RUT", "600519.SS", "2328.HK", "159901.SZ", "000001.SZ", "600019.SS", "601857.SS", "0941.HK", "0241.HK", "045340.KQ", "0215.HK")
frame = c()
for(i in stock_code)
{
  list = BackTest(i, stock_start, stock_end, stock_interval = 'weekly')
  frame = rbind(frame, list$sum_margin)
}
sum = apply(frame, 2, mean)

frame %>% 
  rbind(sum) %>% 
  cbind(c(stock_code, NA)) %>% 
  datatable()

```

## 剧烈下跌：周K： 每月表现

```{r}
stock_code = "000001.SS"
row = c()
for(i in 1:8)
{
  stock_start = paste0("2018-0", i, "-01")
  stock_end = paste0("2018-0", i + 1, "-01")
  list = BackTest(stock_code, stock_start, stock_end, stock_interval = 'weekly')
  row = rbind(row, list$sum_margin)
}

frame = cbind(row, c(1:8))

sum = apply(frame, 2, sum)

frame %>% 
  rbind(sum) %>% 
  datatable()
```

## 月K报告

```{r}
stock_code = "0941.HK"
stock_start = "2012-01-01"
stock_end = "2019-11-07"
list = BackTest(stock_code, stock_start, stock_end, stock_interval = 'monthly')
```

Summary of margin

```{r}
datatable(list$sum_margin)
```

Summary of Stop-loss

```{r}
tryCatch(list$sum_trigger, error = "no stop_loss")
```

Plot of margin

```{r}
list$p_margin
```

Buy and Sell points

```{r}
list$p_points
```

Data

```{r}
datatable(list$data)
```

## 周K报告

```{r}
list = BackTest(stock_code, stock_start, stock_end, stock_interval = 'weekly')
```

Summary of margin

```{r}
datatable(list$sum_margin)
```

Summary of Stop-loss

```{r}
tryCatch(list$sum_trigger, error = "no stop_loss")
```

Plot of margin

```{r}
list$p_margin
```

Buy and Sell points

```{r}
list$p_points
```

Data

```{r}
datatable(list$data)
```

## 日K报告

```{r}
list = BackTest(stock_code, stock_start, stock_end, stock_interval = 'daily')
```

Summary of margin

```{r}
datatable(list$sum_margin)
```

Summary of Stop-loss

```{r}
tryCatch(list$sum_trigger, error = "no stop_loss")
```

Plot of margin

```{r}
list$p_margin
```

Buy and Sell points

```{r}
list$p_points
```

Data

```{r}
datatable(list$data)
```

